Combined annotation exploration for SCPCP000006

### 2025-01-28 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
update params

---
title: "Combined annotation exploration for SCPCP000006"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params:
  predicted.celltype.threshold: 0.75
  cnv_threshold: 0
  testing: 0
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

We simply checked for each chromosome if the cell `has_cnv_chr`.
Would the cell have less than `cnv_threshold` chromosome with CNV, the global `has_cnv_score` will be FALSE.
Would the cell have more than `cnv_threshold` +2 chromosome with CNV, the global `has_cnv_score` will be TRUE.
The default is set to `unknown`.

The `infercnv` method can lead to false positive CNV.
We introduced a flexibility of `+2` over the `cnv_threshold` to reduce the risk of misclassification of normal cells as cancer cells.

@@

```{r fig.width=10, fig.height=10, out.width='100%', results='asis'}
cell_type_df <- cell_type_df |>
  mutate(has_cnv_score = rowSums(cell_type_df[, grepl("has_cnv_chr", colnames(cell_type_df))])) |>
  mutate(has_cnv_score = case_when(
    has_cnv_score > params$cnv_threshold +2 ~ "CNV",
    has_cnv_score <= params$cnv_threshold ~ "no CNV",
    .default = "unknown"
  ))

@@

The threshold used for the `predicted.score` is defined as a parameter of this notebook as `r params$predicted.celltype.threshold`.
The threshold used for the identification of CNV is also defined as the notebook parameter `r params$cnv_threshold`.

>>>>

---
title: "Combined annotation exploration for SCPCP000006"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params:
  predicted.celltype.threshold: 0.85
  cnv_threshold_low: 0
  cnv_threshold_high: 2
  testing: 0
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

We simply checked for each chromosome if the cell `has_cnv_chr`.
Would the cell have less than `r params$cnv_threshold_low` chromosome with CNV, the global `has_cnv_score` will be FALSE.
Would the cell have more than `r params$cnv_threshold_high`  chromosome with CNV, the global `has_cnv_score` will be TRUE.
The default is set to `unknown`.

The `infercnv` method can lead to false positive CNV.
We introduced a flexibility of +`r params$cnv_threshold_high` over the `cnv_threshold` to reduce the risk of misclassification of normal cells as cancer cells.

@@

```{r fig.width=10, fig.height=10, out.width='100%', results='asis'}
cell_type_df <- cell_type_df |>
  mutate(has_cnv_score = rowSums(cell_type_df[, grepl("has_cnv_chr", colnames(cell_type_df))])) |>
  mutate(has_cnv_score = case_when(
    has_cnv_score > params$cnv_threshold_high ~ "CNV",
    has_cnv_score <= params$cnv_threshold_low ~ "no CNV",
    .default = "unknown"
  ))

@@

The threshold used for the `predicted.score` is defined as a parameter of this notebook as `r params$predicted.celltype.threshold`.
The thresholds used for the identification of CNV are also defined as notebook parameters with a minimum of `r params$cnv_threshold_low` and a maximum of `r params$cnv_threshold_high`.
